\thesistitle

### 2019-07-25 sections/introduction.tex
Outline

\section{Outline}
\todo{Rewrite this part}
In Chapter~\ref{ch:background} we describe the background of this thesis.
Chapter~\ref{ch:research} describes ...
Results are shown in Chapter~\ref{ch:results} and discussed in Chapter~\ref{ch:discussion}. Chapter~\ref{ch:related_work}, contains the work related to this thesis.
Finally, we present our concluding remarks in Chapter~\ref{ch:conclusion} together with future work.

>>>>

\section{Outline}
\todo{Rewrite this part}
In Chapter~\ref{ch:background} we describe the background of this thesis. In Chapter~\ref{chap:clonetypes} we list shortcomings with clone definitions from literature and propose a set of clone type definitions which can be automatically refactored. In Chapter \ref{ch:clonerefactor} we propose a tool to detect, analyze and automatically refactor such clones that can be refactored. Using this tool we perform a set of experiments, of which the results are shown in Chapter~\ref{ch:results} and discussed in Chapter~\ref{ch:discussion}. Chapter~\ref{ch:related_work} contains the work related to this thesis. Finally, we present our concluding remarks in Chapter~\ref{ch:conclusion} together with future work.
